Final paper: Towards Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-05-02 paper/paper.tex
paper: quick paragraph about range-based indexing

>>>>

\paragraph{Range-based indexing} See \S~\ref{S:ranged_indexing} for details on
range-based indexing. Our initial attempt, though incomplete, defines a type for
the different types of range indexers and a function for indexing a sub-matrix
via a list of range indexers. We also make use of an auxiliary data function to
convert a list of options to an optional list, which we have proven
correct\footnote{The result is \(\func{None}\) if there is a \(\func{None}\)
anywhere in the list. The result is a list of values if-and-only-if the two
lists have the same length and they agree on the values at all possible
indices.}.
